An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2022-05-09 simplified_sdc_intro/paper.tex
some updates

%\documentclass[times,modern]{aastex63}
%\documentclass[times,preprint]{aastex63}
\documentclass{aastex63}

@@

\author[0000-0002-1530-781X]{Alice Harpole}
\affiliation{Dept.\ of Physics and Astronomy, Stony Brook University,
             Stony Brook, NY 11794-3800}

\author{Melissa Rasmussen}

@@

\acknowledgements \castro\ is freely available at
\url{http://github.com/AMReX-Astro/Castro}.  All of the code and problem setups
used here are available in the git repo.  The double detonation problem is in
{\tt Castro/Exec/science/subchandra}.  The work at Stony Brook was supported by
DOE/Office of Nuclear Physics grant DE-FG02-87ER40317.  This material is based
upon work supported by the U.S. Department of Energy, Office of Science, Office
of Advanced Scientific Computing Research and Office of Nuclear Physics,
Scientific Discovery through Advanced Computing (SciDAC) program under Award
Number DE-SC0017955.  This research was supported by the Exascale Computing
Project (17-SC-20-SC), a collaborative effort of the U.S. Department of Energy
Office of Science and the National Nuclear Security Administration.  This
research used resources of the National Energy Research Scientific Computing
Center (NERSC), a U.S. Department of Energy Office of Science User Facility
located at Lawrence Berkeley National Laboratory, operated under Contract No.
DE-AC02-05CH11231 using NERSC award NP-ERCAP0020354.

\software{\amrex\ \citep{amrex_joss},
          \castro\ \citep{castro},
          GNU Compiler Collection (\url{https://gcc.gnu.org/}),
          Linux (\url{https://www.kernel.org}),
          matplotlib (\citealt{Hunter:2007},  \url{http://matplotlib.org/})
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}),
          \pynucastro\ \citep{pynucastro},
          SymPy \citep{sympy}
         }

>>>>

%\documentclass[times,modern]{aastex63}
\documentclass[times,preprint]{aastex63}
%\documentclass{aastex63}

@@

\author[0000-0002-1530-781X]{A.~Harpole}
\affiliation{Dept.\ of Physics and Astronomy, Stony Brook University,
  Stony Brook, NY 11794-3800}

\author{M.~Rasmussen}
\affiliation{Utah State University, Logan UT 84322}

@@

\acknowledgements \castro\ is freely available at
\url{http://github.com/AMReX-Astro/Castro}.  All of the code and problem setups
used here are available in the git repo.  The double detonation problem is in
{\tt Castro/Exec/science/subchandra}.  The work at Stony Brook was supported by
DOE/Office of Nuclear Physics grant DE-FG02-87ER40317.  This material is based
upon work supported by the U.S. Department of Energy, Office of Science, Office
of Advanced Scientific Computing Research and Office of Nuclear Physics,
Scientific Discovery through Advanced Computing (SciDAC) program under Award
Number DE-SC0017955.  This research was supported by the Exascale Computing
Project (17-SC-20-SC), a collaborative effort of the U.S. Department of Energy
Office of Science and the National Nuclear Security Administration.  MR was supported
via an NSF REU grant to Stony Brook, NSF 1852143.  This
research used resources of the National Energy Research Scientific Computing
Center (NERSC), a U.S. Department of Energy Office of Science User Facility
located at Lawrence Berkeley National Laboratory, operated under Contract No.\
DE-AC02-05CH11231 using NERSC award NP-ERCAP0020354.

\software{\amrex\ \citep{amrex_joss},
          \castro\ \citep{castro},
          GNU Compiler Collection (\url{https://gcc.gnu.org/}),
          Linux (\url{https://www.kernel.org}),
          matplotlib (\citealt{Hunter:2007},  \url{http://matplotlib.org/}),
          NetworkX \citep{networkx},
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}),
          \pynucastro\ \citep{pynucastro},
          pytest \citep{pytest},
          SymPy \citep{sympy},
          yt \citep{yt}
         }
